paper

### 2022-03-28 outputs/paper.Rmd
Update paper.Rmd

>>>>

# Results

# Mother's education

```{r motheredu, echo=FALSE, fig.cap="Mother's Education level"}
mother_edu <-
  ghana %>%
  filter(character=="Mother\'s_education") %>%
  mutate(
    background = factor(background,
                        levels = c('No_education',
                                   'Primary',
                                   'Middle',
                                   'Secondary+')
    )
  )

mother_edu %>%
  ggplot(mapping=aes(x=background, y=number_of_employed_women, fill=background)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  geom_text(aes(label=paste(round(number_of_employed_women/sum(number_of_employed_women),4)*100, '%')), size=4, position=position_stack(vjust = 0.5)) +
  theme_minimal() +
  labs(x='education level',y='count') +
  theme(legend.position='none')
```
